---
title: "ISLA comparison: Visualizing Proportion significant P-values across ROIs"
author: "Virgilio Gonzenbach"
date: "6/18/2021"
output:
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      cache=TRUE, 
                      fig.width = 10, 
                      fig.height = 7, 
                      dpi=300)

knitr::opts_knit$set(root.dir = '/home/vgonzenb/ISLA/')
```

```{r, include=FALSE}
 # Set to my library
myPaths = c(.libPaths(), "/home/vgonzenb/R/x86_64-pc-linux-gnu-library/4.0")
.libPaths(myPaths)
library(ggplot2)
library(plyr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggthemes)
library(gridExtra)
library(stargazer)
library(flextable)
library(hash)

# Load data
load_p_df = function(){
  p_df = read.csv('results/frac_sigPs_by_ROI_adjBy10thr.csv')
  colnames(p_df)[1] = "METHOD"
  
  # Separate first column
  p_df$METHOD = c("Uncorrected", "ISLA_R2", "ISLA_R3", "ISLA_R4", "NWC_R2", "NWC_R3", "NWC_R4")
  p_df = tidyr::separate(p_df, METHOD, into = c("method", "radius"), sep="_")
  
  # Prep method
  p_df$method = factor(p_df$method, levels=unique(p_df$method))
  
  # Prep radius
  p_df = p_df[rep(seq_len(nrow(p_df)), times = c(3,1,1,1,1,1,1)), ] # repeat Raw CBF 3 times to match
  p_df[p_df$method == "Uncorrected", "radius"] = c("R2", "R3", "R4") # fill in radius info for Raw CBF
  p_df$radius = factor(p_df$radius) %>% recode_factor(R2 = "R = 2", R3 = "R = 3", R4 = "R = 4") # recode for plotting
  
  return(p_df)
}

load_dict = function(){
  
  # Load ROI dictionary
  dict = readxl::read_xlsx("data/MUSE_ROI_Dict.xlsx", 1)
  s_dict = dict[dict$ROI_INDEX %in% 2:300, ]
  s_dict$ROI_INDEX = paste0("X", s_dict$ROI_INDEX)

  return(s_dict)
}

p_df = load_p_df()
s_dict = load_dict()

thresh_df = read.csv('results/frac_within_threshold_voxels_by_ROI.csv')
roi_class = readRDS('roi_class.rds')


# Split dataframe ROI class
subset_roi_df = function(roi_df, roi_indexes){
  roi_df = p_df %>% select(method, radius, any_of(roi_indexes))
  return(roi_df)
}

get_roi_info = function(roi_index, info=c("name", "side", "tissue")){
  #' Given ROI index return its name 
  if(is.null(s_dict)){
    print("No dictionary in memory") 
    return(NULL)
  }

  cols = c("ROI_NAME", "HEMISPHERE", "TISSUE_SEG")
  names(cols) = c("name", "side", "tissue")

  col = cols[info]
  rows = match(roi_index, s_dict$ROI_INDEX)
  roi_info = unname(unlist(s_dict[rows, col]))
  return(roi_info)
}
```

## Plots: Examining statistical significance across ROIs

```{r}
plot_regions = function(roi_df, title="", x_text_size=7){
  #' Plot barplots of proportion significant Ps in given ROI
    
  df_long = roi_df %>% pivot_longer(!c("method", "radius"), names_to = "ROI", values_to = "PROP. SIG. P-VALUES", names_ptypes = list(ROI = factor()))
  
  # Order ROIs by Raw CBF
  roi_order = df_long$`PROP. SIG. P-VALUES`[df_long$method == "Uncorrected" & df_long$radius == "R = 2"] %>% order(decreasing = TRUE)
  df_long$ROI = factor(df_long$ROI, levels=levels(df_long$ROI)[roi_order])
  
  # Plot
  df_long %>% ggplot(aes(x=ROI, y=`PROP. SIG. P-VALUES`, fill=method)) + geom_bar(position = 'dodge', stat = 'identity') + 
    theme_classic() + 
    scale_fill_calc(name = "Method") + facet_wrap(~radius) + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size=x_text_size)) + 
    ggtitle(title) + theme(plot.title = element_text(hjust = 0.5))
  
}
```

### Frontal (Left)

```{r frontal_l_plot}
frontal_side = get_roi_info(roi_class$Frontal, "side")

# Add new ROI class to roi_class list of indexes
roi_class[["Frontal L"]] = roi_class$Frontal[frontal_side == "Left"]

p_df %>% subset_roi_df(roi_class[["Frontal L"]]) %>% plot_regions(title = "Frontal (Left)", x_text_size = 8)
```

### Frontal (Right)

```{r frontal_r_plot}
roi_class[["Frontal R"]] = roi_class$Frontal[frontal_side == "Right"]
p_df %>% subset_roi_df(roi_class[["Frontal R"]]) %>% plot_regions(title = "Frontal (Right)", x_text_size = 8)
```

### Temporal

```{r temporal_plot}
p_df %>% subset_roi_df(roi_class[["Temporal"]]) %>% plot_regions(title = "Temporal", x_text_size = 9)
```

### Parietal

```{r parietal_plot}
p_df %>% subset_roi_df(roi_class[["Parietal"]]) %>% plot_regions(title = "Parietal", x_text_size = 9)
```

### Occipital

```{r occipital_plot}
p_df %>% subset_roi_df(roi_class[["Occipital"]]) %>% plot_regions(title = "Occipital", 9)
```

### Deep

```{r deep_plot}
p_df %>% subset_roi_df(roi_class[["Deep"]]) %>% plot_regions(title = "Deep", 9)
```

### Limbic

```{r limbic_plot}
p_df %>% subset_roi_df(roi_class[["Limbic"]]) %>% plot_regions(title = "Limbic", 9)
```

## Tables: Examine ROIs

Note: JLF parcellation consists of 135 labels while MUSE has 145 ROIs. TODO: Why is there a discrepancy?
  
  Which MUSE ROIs are not included in JLF parcellation? Most White Matter regions

```{r, results='asis'}
isInJLF = s_dict$ROI_INDEX %in% thresh_df$X

isInMUSE = thresh_df$X %in% s_dict$ROI_INDEX 

#jlf_dict$ROI_INDEX == readr::parse_number(thresh_df$X[!isInMUSE])
#
#isOnlyInJLF = jlf_dict$ROI_INDEX %in% readr::parse_number(thresh_df$X[!isInMUSE])
#jlf_dict[isOnlyInJLF,] # TODO: Figure out what do with this

index_tbl = s_dict[isInJLF, c("ROI_INDEX", "ROI_NAME")] 

start = seq(1,130, by=26)
end = start + 25

index_tbl_cols = data.frame(index_tbl[start[1]:end[1],])
for(i in 2:length(start)){
  index_tbl_cols = data.frame(index_tbl_cols, index_tbl[start[i]:end[i],])
  i = i + 1
}

index_tbl_cols %>% flextable::flextable() %>% set_header_labels(ft,
                                                                values = list(ROI_INDEX = "INDEX",
                                                                              ROI_NAME = "ROI",
                                                                              ROI_INDEX.1 = "INDEX",
                                                                              ROI_NAME.1 = "ROI",
                                                                              ROI_INDEX.2 = "INDEX",
                                                                              ROI_NAME.2 = "ROI",
                                                                              ROI_INDEX.3 = "INDEX",
                                                                              ROI_NAME.3 = "ROI",
                                                                              ROI_INDEX.4 = "INDEX",
                                                                              ROI_NAME.4 = "ROI")) 


```

Which ROIs are in JLF parcellation but not in MUSE ROIs?
  
```{r}
isInMUSE = thresh_df$X %in% s_dict$ROI_INDEX 
thresh_df[!isInMUSE,]
```

Which JLF ROIs are affected most by 10% GMD thresholding? (Pending)

```{r, results='html'}
df_tmp = thresh_df[order(thresh_df$PROP_VOX_ABV10., thresh_df$NVOX_ROI),]
# data.frame(ROI_NAME = s_dict$ROI_NAME[match(df_tmp$X, s_dict$ROI_INDEX)], df_tmp) %>% stargazer()
# TODO: Use flextable

```
